---
title: "DevelopingDataProducts_Week3_Assignment"
author: "Claire Pierreclos"
date: "2/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is my web page presentation using R Markdown that features a plot created with Plotly. 
My webpage is hosted on GitHub Pages. 
My webpage contain the date that I created the document, and a plot created with Plotly. 
This plot represent the number (in millions) of domestic animals in the United States in comparison with France for dogs, cats and mouses.

## My plotly plot

```{r include=TRUE}
library(plotly)

Animals <- c("Dogs", "Cats", "Mouses")
UnitedStates <- c(80, 61, 23)
France <- c(13, 8, 2)
data <- data.frame(Animals, UnitedStates, France)

p <- plot_ly(data, x = ~Animals, y = ~UnitedStates, type = 'bar', name = 'United States') %>%
  add_trace(y = ~France, name = 'France') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'group', title = 'Number of domestic animals (in millions)')
p
```
