---
title: "CompressiveStrenghtConcrete"
author: "Claire Pierreclos"
date: "3/9/2020"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Compressive Strenght Concrete Project

In these slides, you will find my assignment work for the Developing Data Products course in the Data Science specialization on Coursera.

I choose to use the example dataset concrete to plot the data and use some variables.

## Concrete dataset

What is the concrete dataset?
Yeh (1998) describes a collection of data sets from different sources that can be used for modeling the compressive strength of concrete formulations as a functions of their ingredients and age.

The data are from Yeh (1998) and taken from the UCI ML website <http://archive.ics.uci.edu/ml/datasets/Concrete+Compressive+Strength>.

There are 1030 data points from the UCI website, but the paper states that approximately 1,000 samples were made, but only 727 were analyzed in the source material. It is unclear which samples were excluded.

concrete	
data frame of data with predictor columns Cement, BlastFurnaceSlag, FlyAsh, Water, Superplasticizer, CoarseAggregate, FineAggregate and Age with response column CompressiveStrength. These are the amounts.

mixtures	
The same data where all the ingredients have been converted to proportions of the total amounts.

## Concrete contents

```{r concrete, echo = TRUE}
library(AppliedPredictiveModeling)
data(concrete)
summary(concrete)
```

## My shiny plot

```{r shiny}

library(shiny)

# Define UI for application 
ui <- fluidPage(

    # Application title
    titlePanel("Compressive Strength of Concrete from Yeh (1998)"),
    
    # Sidebar with a slider input for number of bins 
    sidebarLayout(
        sidebarPanel(
            sliderInput("pValue",
                        "Percentage of data in the train set",
                        min = 1,
                        max = 100,
                        value = 75),
            checkboxInput("colorUse","Use colors in the plot",value=TRUE),
            selectInput("xVariable", "Type of x variable against which plot:",
                        c("fraction" = "fraction",
                          "penalty" = "penalty",
                          "L1norm" = "L1norm",
                          "step" = "step"))
        ),

        # Show a plot of the generated distribution
        mainPanel(
           plotOutput("concretePlot")
        )
    )
)

# Define server logic required to draw a histogram
server <- function(input, output) {
    
    output$concretePlot <- renderPlot({
     
        # Import needed libraries
        library(caret)
        library(AppliedPredictiveModeling)
        library(elasticnet)
        
        #Set the seed for the reproductible
        set.seed(3523)
        
        # Use sample data concrete
        data(concrete)
        
        # Predictive model
        inTrain = createDataPartition(concrete$CompressiveStrength, p = input$pValue/100)[[1]]
        training = concrete[ inTrain,]
        testing = concrete[-inTrain,]
        fitLs <- train(CompressiveStrength~., data=training, method = "lasso")
        
        # Plot
        plot.enet(fitLs$finalModel, xvar = input$xVariable, use.color = input$colorUse)
        
    })
}

# Run the application 
shinyApp(ui = ui, server = server)


```

